\vspace{1cm}
\section{Revisit your main challenge and refine it and its sub-questions, based 
on your insight statements.}
\label{section_4}

\paragraph{Insight: } 
Users tend to not pay attention to the ISPs terms and agreements regardless of 
the time they have spent on the internet. \\
\\\emph{How might we } 
refine terms and agreements more appealing to users and engage them more to pay 
attention to what they have agreed with?

\paragraph{Insight: }
Users are concerned about their profiling on targeting advertisement. \\
\\\emph{How might we }
restrict profiling to provide targeted advertising only on the services that 
will benefit us, regarding user budget and targeted recommendations (e.g. 
e-shops, airline tickets)?\\
\\\emph{How might we }
have more transparency on the exact information that are extracted to build the 
user profiles and their cost?

\paragraph{Insight: }
A very high percentage of the users do not trust the social media to keep their 
information private.\\
\\\emph{How might we }
inform users better about the risks of sharing sensitive information online?

\paragraph{Insight: }
Even though users are willing to use anonymization tools for their protection on 
the internet, they seem reluctant to pay for such a service.\\
\\\emph{How might we }
develop a reliable service that users can trust for security and privacy?

\paragraph{Insight: }
Users are not fully informed about the implication of laws of each country on 
their data.\\
\\\emph{How might we }
inform users about the existing laws of each country which apply to their online 
data and traffic.

