\section{Create a Pitch!}

\subsection{What is your project?}

Do you know who has access to your personal information? Are you aware of how 
much publicly exposed you are? Are you certain that your data is not being used 
for malicious purposes? There are many third party companies that can obtain 
your sensitive information and collect private data from many of the services 
you provided those data yourself. This can be further used to construct 
advertisements targeted for you or even purposefully create fake profiles using 
parts of your personal information. Are you aware that you are the one who gave 
all those companies permission to do so?

The aforementioned facts are stated in plain sight in every terms and agreements 
document of every online service, even though the words are disguised and 
presented in such ways that are difficult for an average user to extract the 
hidden meanings. Those documents are quite extended on purpose and that is a 
crucial reason users do not spend time on reading them and consequently missing 
those concealed statements. Due to this fact, we aim to improve the transparency 
between client and service provider by enabling users to understand what they 
agree to, by spending as little time as possible in studying the terms and 
agreements that are presented to them.

To achieve this goal, we propose a free browser extension tool, coming as an 
open source idea, that will be compatible with any modern browser (Google 
Chrome, Safari, Opera,Mozilla Firefox, Microsoft Edge) available for downloading 
and easy to use. The core idea is to provide a clear view of the key parts of 
terms and conditions documents that need the attention of the user using a 
simple and straightforward interface. By keeping it simple we facilitate the 
iteration through the document, only focusing on the vital points that most 
probably also contain disguised messages, such as user privacy, public exposure 
and sharing between companies.

On the front end, users will be presented with the exact terms and agreements 
page of each service, enhanced by our tool by highlighting keywords or key 
phrases, providing additional pop up comments for each highlighted section 
containing further explanation or alternative interpretation of each one. On the 
back end there will be a distributed database containing those words and phrases 
in order to be matched with the ones in the document after being identified from 
a plain-text crawler.

The plug-in code will be publicly available in full on a repository such as 
github in order for any developer to contribute to its refinement. In addition, 
any user can also contribute to the project by becoming a member of an open 
community established to update and maintain the database with further keywords 
and comments. The idea behind the community is to provide a user centric 
environment and safer overall feeling, in order to obtain and ensure the user 
trust in using our service. Concluding, our proposition is an ongoing never 
ending process that commits to improve and update along with every online 
service. 

\subsection{Who will you pitch to and for which objective?}

Our plug-in extension tool is going to be pitched to two specific groups. The 
first group that is crucial to  pitch to are the users  

In the first category the target is to engage users to download and install the 
plug-in to their browser. In order to achieve that, our service needs to be 
presented in a certain way, which is going to alert the users about the 
significance of terms and agreements and the impact they have to their privacy. 
Another objective for pitching to the users is to make them immerse in the 
community. This step is important because the service is depending on the help 
of each user for improving the quality of the provided feedback given on terms 
and conditions.

The aspect of funding is another important factor which is going to be crucial 
for the development part of our service. Nowadays, various ways of funding exist 
for developing creative ideas. Our service is targeting a funding from 
KickStarter which can be used to raise the necessary amount of money for the 
starting operational costs. Furthermore, every user can contribute to the 
financial viability of the project by donations. 

\subsection{What is your elevator pitch?}

``Hey! I have a brand new mobile phone. I’ll give it to you for free, do you 
want it? I bet you said yes without a second thought. What if I told you that 
without you noticing, it collects all your personal information? Do you still 
want it? No. Then why do you not pay attention to terms and conditions of use? I 
know it's boring. I can help you! Download and use my plug-in on your browser 
and let it automatically highlight the keywords on those tedious documents. You 
still don't trust me? Then trust the community that contributes to its accuracy 
and improvement with helpful comments. Is it clearer now? You can help others, 
too. Become a member, spread the word.''
