\subsubsection{Key insights} 

\vspace{0.4cm}
\paragraph{Theme:} Privacy and anonymization tools.
\paragraph{Insights:}
\begin{enumerate}
\item
Users regardless of age or education level tend to care about their privacy on 
the internet.
\item
The majority of users believe that there isn't any stringency on user's internet 
data privacy.
\item
Even though users are willing to use anonymization tools for their protection on 
the internet, they seem reluctant to pay for such a service.
\end{enumerate}

%%
\vspace{0.1cm}
\paragraph{Theme:} Routing and Storage. 
\paragraph{Insights:}
\begin{enumerate}
\item
Most of the users seem to be concerned about their traffic routing and data and 
the specific storage locations.
\item
Users want to be more informed about the identity of third party companies 
interceding their communications.
\end{enumerate}

%%
\vspace{0.1cm}
\paragraph{Theme:} Law Enforcements and Regulations.
\paragraph{Insights:}
\begin{enumerate}
\item
Users tend to not pay attention to the ISPs terms and agreements regardless of 
the time they have spent on the internet. 
\item
More than half of users, care a lot about the sharing of their information to 
the law enforcement agencies and government.
\item
Users are not fully informed about the implication of laws of each country on 
their data.
\end{enumerate}

%%
\vspace{0.1cm}
\paragraph{Theme:} Economy and Advertising. 
\paragraph{Insights:}
\begin{enumerate}
\item
Users are fully aware of the existence of targeted advertising on the internet.
\item
Users are aware about profiling mechanisms on targeted advertising, and they are 
concerned about being the product of the internet advertising companies. 
\end{enumerate}

%%
\vspace{0.1cm}
\paragraph{Theme:} User Trust. 
\paragraph{Insights:}
\begin{enumerate}
\item
Most of the users tend to not trust the ISPs with handling their personal 
information.
\item
A very high percentage of the users do not trust the social media to keep their 
information private.
\end{enumerate}

