\subsection{The idea}

\paragraph{Design challenge} 

Refinement of terms and conditions in order to 
make them easier to read and more appealing to the users.

\paragraph{HMW Question} 

How might we make terms and conditions more legible 
for the casual users?

\paragraph{Description}

Our system is based on the  open source idea, not only in the development part 
but also on the community part. The service is able to identify the important 
parts of terms and agreement by using a distributed database containing keywords.
This database is maintained and updated by whoever is part of the community. 
Specifically we are going to develop a plug-in to run on any web browser.
Whenever the user wants to analyze terms and agreements of a service, he 
executes the plug-in. The plug-in uses a web crawler to retrieve the plain text, 
and does a request to the database for every word recognized on the text. If a 
word is identified as a keyword, the sentence containing it is highlighted. At 
the same time if the community has committed any comment for the given keyword 
or sentence, it will be displayed along with the highlights on a pop up bubble 
notification.
The comments might contain explanations on law sections or on other parts that 
need redefinition.

\paragraph{Ideas Impact on the Challenge}

We learnt that people hardly pay attention to terms and conditions upon the 
signing up procedure. As a result, they end up agreeing to those terms and 
conditions, without even knowing the consequences on their privacy. 
This idea allows users to easily read and understand the terms and conditions 
that they ought to agree to, in order to have access to a certain service.  
This solution will be deployed as a browser add-on. The users should download 
and install the add-on. Each time they want to sign up to a service, the users 
will be able to read the terms-and-conditions section in a more structured 
manner, something that will make the comprehension of their agreements easier. 
That way, users will be more aware of the rights they give to each service 
concerning their data. This will result to more transparency on where their 
personal information is forwarded and how that affects them. In addition, a 
community is supposed to be established that will be responsible for the update 
and maintenance of our add-on.  
