\subsection{Solutions} 

\paragraph{Solution 1: Refinement of terms and conditions in order to make them 
easier to read and more appealing to the users.} 
How to: Provide an add-on service that, by using a database containing keywords 
that are most commonly used in such documents, highlights those words in the 
terms and conditions document that each online service provides. In addition, as 
a further step, a user community will be established with the goal to refine 
such documents, and present them in parallel with the original document. The 
aforementioned refinement will provide the same document written in simpler 
words, to help users with little to no experience with law terms understand 
better the conditions they are asked to agree with.

\paragraph{Solution 2: Inform users about the risks of sharing sensitive and 
private information on social media and on online services in general.} 
How to: Produce a public video, available for sharing, that shows in a direct 
way how much private information can be collected for a random individual, just 
by peeking at his social media profiles. In this video, the lead actor will be a 
``mind reader'' who will offer to read a random passers by mind. At the same 
time a hidden assistant, after hearing the name of the ``victim'' will search to 
find every possible information he can and provide them by hidden earpiece to 
the ``mind reader'', who subsequently will present them as findings from reading 
the ``victim's'' mind. After the session is over, the hidden assistant will be 
revealed to make the ``victim'' realise that he was exposed through the stuff he 
willingly posted online.

\paragraph{Solution 3: Transparency on the user's information that can be 
extracted and used for profiling and how much they cost.} 
How to: Provide an add-on service, that every time you press/run it, it will gain 
all information it can extract from you and represent them in a table. This 
information will include your IP address, location, operation system, your 
personal computer's technical characteristics, the browser you use, search 
history, the online services you are currently logged in etc. In addition, this 
service will communicate with another, already existing service, that can 
compute the cost of an individual's personal information, and provide this as 
well.

