The main purpose of this project is to deploy an approach on how might we have
more transparency on where our data is going in the Internet.  
Through the design thinking process, we proceed via the phases of inspiration, 
ideation and implementation, in order to complete the goal of the challenge.

Firstly, in the chapter of \emph{inspiration}, we aim to understand the topic of 
the challenge, by specifying the corresponding ground truth, the aspects that we 
are not familiar with and also, the difficulties that expect to face in the 
process of our work. In addition, we conduct a primary research, that includes 
the development and the analysis of a user survey, an interview with an expert 
of the field and the study of well-known analogous examples. Finally, we do the 
necessary bibliographic examination for the secondary research.

In the following chapter --\emph{ideation}--, we present the questionnaire and 
interview results and findings, the key insights and the refining challenges,
regarding the \emph{synthesis phase}. In the second phase of ideation 
--\emph{prototype}--, we present multiple possible solutions for the stated 
problem. However, in order to proceed, we end up selecting a single solution
for the challenge and then, we unwrap this idea. This work includes a storyboard,
mock-ups, and the evaluation of our prototype. Moreover, in this section, we 
reexamine our prototype by utilizing the feedback that we received and we present
the updated one. 

In the last part of this work, \emph{implementation}, we present the 
necessary action plan for our product and finally, the pitch.
